Please Read the Abstract

### 2018-05-21 Draft/thesis-ku.tex
may 21

@@

@@

%% The following is OPTIONAL. Remove all 3 of the next 3 lines
%% to leave dates blank. If dates are included, then both dates 
%% must be included.
\@printd@testrue
\datedefended{October 02, 2012}
\dateapproved{October 03, 2012}

@@

\maketitle
\begin{abstract}
Version 2.1, May 20, 2013. This was a minor update that slightly changed
kuthesis.cls. First, the Graduate School no longer exists, so we rephrase
the front matter to refer to Graduate Faculty. Second, the page numbering
after the front matter begins at arabic number 1. This was an oversight
in the previous edition, it was never intended, but users found easy
``work arounds'' and we were not aware of it.

Version 2, October 2, 2012. This is a minor update to allow insertion
of dates in the document preamble.

If you are reading the pdf, this document is produced from ``thesis-ku.tex''
using the \LaTeX{} class kuthesis.cls and other common packages that
are almost surely installed in a working \LaTeX{} system. We suggest
you try to compile this document in your system (as a test), and after
that use it as a template for your project.

\textbf{Look here.} The \LaTeX{} class ``kuthesis.cls'' extends
the base class called ``report''. If you have a report document
already, migration into this format will be easy, since we inherit
everything from ``report'' and then customize a few things.

\textbf{How To Use? }This is a basic \LaTeX{} usage question. You
need a ``\LaTeX{} distribution'' such as TexLive or MikTex. You
need to run the file thesis-ku.tex through the \LaTeX{} processing
system. At the current time, the preferred output format is pdf from
the ``pdflatex'' program, but it is probably safe to try other programs
as well. On most \LaTeX{} systems, your latex processor will look
in several places for ``kuthesis.cls'' while it processes thesis-ku.tex.
Usually, you don't need to install formally that file, since--on most
systems--the \LaTeX{} program will look in the current working directory
for syle files. If so, then this document will ``just work'' for
you. If you want to use kuthesis.cls for several documents, you need
to either copy it into every document directory, or install ``kuthesis.cls''
in a place where your \LaTeX{} system will find it, and then run the
\LaTeX{} re-configurator to make the system notice. In my system,
\LaTeX{} is set up to look in /usr/share/texmf/tex/latex, /usr/local/share/texmf/tex/latex,
as well as in my home directory and the current working directory.
I copy kuthesis.sty into /usr/local/share/texmf/tex/latex, run the
re-configurator program ``texhash,'' and it is ready to go.

\textbf{Does it work with Lyx?} Yes, as a matter of fact, I'm preparing
this document in \LyX{} right now. (\LyX{} is a GUI \LaTeX{} document
editor, available for free at \url{http://www.lyx.org}.) \LyX{} will
open the document, but it will warn that the layout file ``kuthesis.layout''
is unavailable. Unfortunately, the only fix for that is to install
the customized layout file, which is provided with this document in
the stylefiles directory. Copy the kuthesis.layout file into the one
of the folders where \LyX{} looks for layout configurations. I did
not install that in the system-wide \LyX{} layout folder, but rather
in my personal user configuration folder. I suggest you so the same,
at least while you are testing this. On Linux, that is in the user
HOME under .lyx/layouts. (For me, that's ``/home/pauljohn/.lyx/layouts.''
On other OS, here's how you can find out where to put the layout.
Run \LyX{}, in the top menu choose Tools/Preferences. Change something
trivial, close. That will force \LyX{} to create a user folder somewhere
in your personal HOME directories. In MS Windows 7, I just tested
this. I searched for the word ``layouts'' and found my \LyX{} preference
folder is ``C:\textbackslash{}Users\textbackslash{}pauljohn\textbackslash{}AppData\textbackslash{}Roaming\textbackslash{}lyx202\textbackslash{}layouts''.

\textbf{Note.} To customize this document, you have to edit the document
preamble to put in your name, title, degree name, department, and
advisors. If you don't do that, you won't get the right title page.
To be explicit, in this document, the following values are currently
set in the preamble:

\begin{minipage}[t]{1\columnwidth}%
\inputencoding{latin9}\begin{lstlisting}
\title{Please Read the Abstract} 
\author{Abstract Writer} 
\dept{Department of People who read Abstracts} 
\degreetitle{Doctor of Philosophy} 
\papertype{Dissertation} %capitalization is important here 
\committee{MEMBER 1}{MEMBER 2}{MEMBER 3}{MEMBER 4}{}
\end{lstlisting}
\inputencoding{utf8}%
\end{minipage}

\textbf{Note please.} Replace ``Member 1'' with a name, of course.
You can have at most 5 committee members, but you can have fewer.
For the ones you have, put their names inside squiggles; for the ones
you don't want, leave empty squiggles, \{\}, as I've demonstrated
on the 5th member in this example.

\textbf{Note also. }The chapters included here are just for illustration
and testing. I've fiddled the format to look like what KU asks for.

\textbf{Note also. }Note the file ``thesis-ku.tex'' (or thesis-ku.lyx,
as the case may be), does not have much content. It has the title
page, the abstract, and not much else. Everything else is brought
in from separate files. I strongly recommend you keep separate chapters
in separate folders. If you don't do that, you will likely go insane.

\textbf{Note for the version 2012-10-02.} In the first edition of
this setup, I left the dates blank and expected users to write or
type them in as necessary. A user requested a fix to allow the dates
of the defense and final approval to be added in the document preamble
with the other settings. So in the end of the document preamble, insert
the following. The first is some \LaTeX{} code, don't change it.

\begin{minipage}[t]{1\columnwidth}%
\inputencoding{latin9}\begin{lstlisting}
\@printd@testrue
\datedefended{October 2, 2012}
\dateapproved{October 3, 2012}
\end{lstlisting}
\inputencoding{utf8}%
\end{minipage}

\textbf{Note finally.} I want you to use \LaTeX{} to prepare documents.
Doing anything else is ``finger painting.'' But don't ask me for
much help. If you find something wrong with kuthesis.cls, I will be
glad to try to fix it if you let me know. I don't have time/ability
to answer a million email questions about \LaTeX{} or \LyX{}. So please
consult the WWW, there is a ton of stuff up there, that's how I learned.
And if you get in a serious hole and ask me for help, it might cost
you a t-shirt.

Paul Johnson <pauljohn@ku.edu>

Prof. Political Science \& Assoc. Dir., Center for Research Methods
and Data Analysis

2012-10-02

And that's the end of the abstract.

@@

I would like to thank mum, dad, Prof. Shandarin, committee members, officemates, friends, exes, uncles, aunts, grandpa, grandma, grandma's dogs, neighbors, neighbors' dogs who made this thesis possible.

@@

\include{Chapter1/intro}
\include{Chapter2/background}
\include{Chapter3/Paper2015}
\include{Chapter4/Paper2017a_Nobmath}
\include{Chapter5/Paper2017b_Nobmath}

@@

\bibliographystyle{apalike2}
%\bibliography{Biblio/allcites}
\bibliography{Biblio/library2018}

\appendix
\include{Appendix1/Appendix1}
\include{Appendix2/Appendix_paper2017a}
\include{Appendix3/Appendix_paper2017b}

>>>>

%%%%%% FROM Comparison Paper2018

\usepackage{url, amsmath,epsfig,epstopdf}
%\usepackage{url,ulem,amsmath,amsfonts,amssymb,epsfig,epstopdf}
%\usepackage{times}
\usepackage{graphicx}
% input macros for figures
\usepackage{epsf}
%\usepackage{bm}
\usepackage{color}
\usepackage{rotating}
\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}
\usepackage{array,multirow}
%\usepackage[percent]{overpic}

%\usepackage[round]{natbib}
% Symbol definitions
%\bibliographystyle{mnras}
\usepackage{aas_macros}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{txfonts}
%\usepackage[draft]{hyperref}

@@

%%%%%% FROM Comparison Paper2018

\newcommand{\Mspace}         {{{\mathbb M}}}

\newcommand{\nil}[1]{\textcolor{red}{\bf NL: #1}}
\newcommand{\bridget}[1]{\textcolor{green}{\bf BF: #1}}
\newcommand{\mc}[1]{\textcolor{red}{\bf #1}}
\newcommand{\elmo}[1]{\textcolor{magenta}{\bf ET: #1}}

\newcommand{\NEW}[1]{\textcolor{blue}{  #1}}
\newcommand{\mcd}[1]{\textcolor{red}{\sout{  #1}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        The names of the methods
\newcommand{\bisous}{Bisous}
\newcommand{\classic}{\textsc{CLASSIC}}
\newcommand{\disperse}{\textsc{DisPerSE}}
\newcommand{\fine}{\textsc{FINE}}
\newcommand{\origami}{\textsc{ORIGAMI}}
\newcommand{\mst}{\textsc{MST}}
\newcommand{\dtfe}{\textsc{DTFE}}
\newcommand{\Nexus}{\textsc{NEXUS}}
\newcommand{\nexus}{\textsc{NEXUS+}}
\newcommand{\tweb}{T-web}
\newcommand{\vweb}{V-web}
\newcommand{\mswa}{\textsc{MSWA}}
\newcommand{\mmft}{\textsc{MMF-2}}
\newcommand{\spine}{Spineweb}
\newcommand{\logFilter}{Log-Gaussian}
\newcommand{\Vector}[1]{\mathbf{#1}}

@@

%% The following is OPTIONAL. Remove all 3 of the next 3 lines
%% to leave dates blank. If dates are included, then both dates 
%% must be included.
\@printd@testrue
\datedefended{October 02, 2018}
\dateapproved{October 03, 2018}

@@

\maketitle
\begin{abstract}

% 2015 Paper
We report the results of the first study of the multi-stream environment of dark matter haloes in cosmological N-body simulations
in the $\Lambda$CDM cosmology. The full dynamical state of  dark matter can be described as a three-dimensional sub-manifold
in six-dimensional phase space - the dark matter sheet. In our study we use a Lagrangian sub-manifold ${\bf x} = {\bf x}({\bf q},t)$ 
(where {\bf x} and {\bf q} are co-moving Eulerian and Lagrangian coordinates respectively), which 
is dynamically  equivalent to the dark matter sheet but is more convenient for numerical analysis.
Our major results can be summarized as follows. At the resolution of the simulation i.e. without additional
smoothing, the cosmic web represents a hierarchical structure: each halo is embedded in the filamentary framework of the web predominantly 
at the filament crossings, 
and each filament is embedded in the wall like fabric of the web at the wall crossings. 
Locally, each halo or sub-halo is a peak in the number of streams field. The number of streams in the neighbouring  
filaments is higher than in the neighbouring walls. The walls are regions where number of streams
 is equal to three or a few. Voids are uniquely defined by the local condition requiring to be a single-stream flow region.
  The shells of streams 
 around haloes are  quite thin and the closest void region is typically within one and a half FOF radius 
 from the center of the halo.

% 2017 Paper_b
Mysterious dark matter constitutes about 85\% of all mass in the Universe. Clustering of dark matter plays the dominant role in the formation of all observed structures on scales from a fraction to a few hundreds of Mega-parsecs. Galaxies play a role of lights illuminating these structures so they can be observed. The observations in the last several decades have unveiled opulent geometry of these structures currently known as the cosmic web. Haloes are the highest concentrations of dark matter and host luminous galaxies. Currently the most accurate modeling of dark matter haloes is achieved in cosmological N-body simulations. Identifying the haloes from the distribution of particles in N-body simulations is one of the problems attracting both considerable interest and efforts. We propose a novel framework for detecting potential dark matter haloes using the field unique for dark matter  -- multistream field. The multistream field emerges at the nonlinear stage of the growth of perturbations because the dark matter is collisionless. Counting the number of velocity streams in gravitational collapses supplements our knowledge of spatial clustering. We assume that the virialized haloes have convex boundaries. Closed and convex regions of the multistream field are hence isolated by imposing a positivity condition on all three eigenvalues of the Hessian estimated on the smoothed multistream field. In a single-scale analysis of high multistream field resolution and low softening length, the halo substructures with local multistream maxima are isolated as individual halo sites.

% 2017 Paper_a
Topological connections in the single-streaming voids and multistreaming filaments and walls reveal a cosmic web structure different from traditional mass density fields. A single void structure not only percolates the multistream field in all the directions, but also occupies over 99 per cent of all the single-streaming regions. Sub-grid analyses on scales smaller than simulation resolution reveal tiny pockets of voids that are isolated by membranes of the structure. For the multistreaming excursion sets, the percolating structure is significantly  thinner than the filaments in over-density excursion approach.

Hessian eigenvalues of the multistream field are used as local geometrical indicators of dark matter structures. Single-streaming regions have most of the zero eigenvalues. Parameter-free conditions on the eigenvalues in the multistream region may be used to delineate primitive geometries with concavities corresponding to filaments, walls and haloes.

% \begin{minipage}[t]{1\columnwidth}%
% \inputencoding{latin9}\begin{lstlisting}
% \title{Please Read the Abstract} 
% \author{Abstract Writer} 
% \dept{Department of People who read Abstracts} 
% \degreetitle{Doctor of Philosophy} 
% \papertype{Dissertation} %capitalization is important here 
% \committee{MEMBER 1}{MEMBER 2}{MEMBER 3}{MEMBER 4}{}
% \end{lstlisting}
% \inputencoding{utf8}%
% \end{minipage}

% 2018 Paper
The cosmic web is one of the most striking features of the distribution of galaxies and dark matter on the largest scales in the Universe. It is composed of dense regions packed full of galaxies, long filamentary bridges, flattened sheets and vast low density voids. The study of the cosmic web has focused primarily on the identification of such features, and on understanding the environmental effects on galaxy formation and halo assembly. As such, a variety of different methods have been devised to classify the cosmic web -- depending on the data at hand, be it numerical simulations, large sky surveys or other. In this paper we bring twelve of these methods together and apply them to the same data set in order to understand how they compare. In general these cosmic web classifiers have been designed with different cosmological goals in mind, and to study different questions. Therefore one would not {\it a priori} expect agreement between different techniques however, many of these methods do converge on the identification of specific features. In this paper we study the agreements and disparities of the different methods. For example, each method finds that knots inhabit higher density regions than filaments, etc. and that voids have the lowest densities. For a given web environment, we find substantial overlap in the density range assigned by each web classification scheme. We also compare classifications on a halo-by-halo basis; for example, we find that 9 of 12 methods classify around a third of group-mass haloes (i.e. $M_{\rm halo}\sim10^{13.5}h^{-1}M_{\odot}$) as being in filaments. Lastly, so that any future cosmic web classification scheme can be compared to the 12 methods used here, we have made all the data used in this paper public.

% \begin{minipage}[t]{1\columnwidth}%
% \inputencoding{latin9}\begin{lstlisting}
% \@printd@testrue
% \datedefended{October 2, 2012}
% \dateapproved{October 3, 2012}
% \end{lstlisting}
% \inputencoding{utf8}%
% \end{minipage}

@@

I would like to thank mum, dad, profs, committee members, officemates, friends, exes, uncles, aunts, grandpa, grandma, grandma's dogs, neighbors, neighbors' dogs who made this thesis possible.

@@

\include{Chapter1/intro}
\include{Chapter2/background}
\include{Chapter3/Paper2015}
\include{Chapter3b/Paper2018}
\include{Chapter4/Paper2017a_Nobmath}
\include{Chapter5/Paper2017b_Nobmath}
\include{Chapter6/concl}

@@

\bibliographystyle{apalike2}
%\bibliography{Biblio/allcites}
\bibliography{Biblio/library}

\appendix
% \include{Appendix1/Appendix1}
\include{Appendix2/Appendix_paper2017a}
\include{Appendix3/Appendix_paper2017b}
